Asymmetric relationships and their effects on coexistence: Supporting information

### 2023-03-23 paper/SupMat.Rnw
pretty complete job editing for now, just waiting for Jasmin's figure work to complete my editing

@@

%***DAN: The code does not yet produce this figure. Eventually it needs to.
%NOTE: I have assumed this figure will look substantially the same as the corresponding main text 
%figure when I wrote the Results. If it does not, then some revisions will be needed.
\begin{figure}
\includegraphics[width=\textwidth]{../results_figs/decompFigLBqij.pdf}
\caption[Analogous to Fig. \ref{MT-fig:fig4} but making a different choice for $q_{ij}$]
{Analogous to Fig. \ref{MT-fig:fig4} of the main text, but using 
$q_{ij}=\eta_i/(\eta_j(1-\delta)+\eta_i \delta)$. See the caption of
that figure for details. Standard errors of plotted quantities 
were never greater than \Sexpr{round(se4qij,5)}, so are not displayed.}\label{fig:fig4_alt}
%***DAN: jasmin, once the se is generated and saved by your code, the chunk at the outset of this 
%document needs to be modified to load that quantity, and then the 0 in the above expression 
%needs to be replaced by the variable name used.
%***JAS:done
\end{figure}

>>>>

\section{    Three-way decompositions}\label{sect:threeway}

As mentioned in the Discussion in the main text, \cite{Ellner_2019} elaborated 
a general theory in which more and different varying factors than
$E$ and $C$ can be considered and used to produce a decomposition of GWR. For instance, if $X$, $Y$ and 
$Z$ are temporally varying factors, \cite{Ellner_2019} produced, for the $i^{\text{th}}$ species, the decomposition
\begin{align}
\text{GWR}_i &= \Delta_i^0+\Delta_i^X+\Delta_i^Y+\Delta_i^Z \label{eq:9}\\
&+\Delta_i^{(X \shp Y)} +\Delta_i^{(XY)} + \Delta_i^{(Y \shp Z)} + \Delta_i^{(YZ)} +\Delta_i^{(X \shp Z)}+\Delta_i^{(XZ)} \label{eq:10}\\
&+ \Delta_i^{(XYZ)}+\Delta_i^{(XY \shp Z)}+\Delta_i^{(X \shp YZ)}+\Delta_i^{(XZ \shp Y)}+\Delta_i^{(X \shp Y \shp Z)}.\label{eq:11}
\end{align}
The terms in (\ref{eq:9}) and (\ref{eq:10}) are analogous to those of main text equations (\ref{MT-eq:previous_decomp}).
The new terms in (\ref{eq:11}) result from rendering one or 
more of $X$, $Y$, and $Z$ independent of the others.
We simply comment that this general decomposition should also be extendable to consider the effects of
ATAs in the same way main text equation (\ref{MT-eq:full_decomp}) extends main text equation (\ref{MT-eq:previous_decomp}), 
though the complexity
of such a decomposition may present challenges.
For example, $\Delta^{(XY \shp Z)}$ can be decomposed as $\Delta^{[XY \shp Z]} + \Delta^{[X \nat Y \shp Z]}$.

@@

\begin{figure}
\includegraphics[width=\textwidth]{../results_figs/decompFigLBqij.pdf}
\caption[Analogous to Fig. \ref{MT-fig:fig4} but making a different choice for $q_{ij}$]
{Analogous to Fig. \ref{MT-fig:fig4} of the main text, but using 
$q_{ij}=\eta_i/(\eta_j(1-\delta)+\eta_i \delta)$. See the caption of
that figure for details. Standard errors of plotted quantities 
were never greater than \Sexpr{round(se4qij,5)}, so are not displayed.}\label{fig:fig4_alt}
%***DAN: jasmin, once the se is generated and saved by your code, the chunk at the outset of this 
%document needs to be modified to load that quantity, and then the 0 in the above expression 
%needs to be replaced by the variable name used.
%***JAS:done
\end{figure}
